---
title: "influxdbr"
output: github_document  
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
Sys.setenv(LANG = "en")
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/influxdbr)](https://cran.r-project.org/package=influxdbr) [![Build Status](https://travis-ci.org/dleutnant/influxdbr.svg?branch=master)](https://travis-ci.org/dleutnant/influxdbr)

R interface to [InfluxDB](https://docs.influxdata.com/influxdb)

This package allows you to fetch and write time series data from/to an InfluxDB server.
Additionally, handy wrappers for the Influx Query Language (IQL) to manage and explore a remote database are provided.

## Installation

Installation is easy thanks to CRAN:
```{r cran, eval = FALSE}
install.packages("influxdbr")
```

You can install the dev version from github with:
```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("dleutnant/influxdbr")
```

## Example

This is a basic example which shows you how to communicate (i.e. query and write data)
with the InfluxDB server.

```{r libs}
library(dplyr)
library(influxdbr)
library(xts)
```

Let's create first some sample data from the xts package and assign arbitrary 
attributes:

```{r sample}
# attach data "sample_matrix"
data("sample_matrix")

# create xts object
xts_data <- xts::as.xts(x = sample_matrix)

# assign some attributes
xts::xtsAttributes(xts_data) <- list(info = "SampleDataMatrix",
                                     UnitTesting = TRUE, 
                                     n = 180,
                                     source = "xts")
                                     
# print structure to inspect the object
str(xts_data)
```

### InfluxDB connection

To connect to an InfluxDB server, we need a connection object. A connection object 
can be created by providing usual server details (e.g. `host`, `port`, ...) or with
help of a group file, which conveniently holds all information for us (s. package 
documentation):

```{r connection}
# create connection object 
# (here: based on a config file with group "admin" in it (s. package documentation))
con <- influx_connection(group = "admin")
```

The `influxdbr` package provides handy wrappers to manage a remote InfluxDB:

```{r db_management}
# create new database
create_database(con = con, db = "mydb")

# list all databases
show_databases(con = con) %>% 
  filter(name == "mydb") # show the db created above only
```
### Write data

#### xts

Writing an xts-object to the server can be achieved with `influx_write`. In this 
case, columnnames of the `xts` object are used as InfluxDB's field keys,
`xts`'s coredata represent field values. Attributes are preserved and written
as tag keys and values, respectively.

```{r write_xts}
# write example xts-object to database
influx_write(con = con, 
             db = "mydb",
             x = xts_data, 
             measurement = "sampledata")
```

#### data.frame

Writing a data.frame (or tibble) to the server can also be achieved with
`influx_write`. In this case, we need to specify which columns of the data.frame 
represent time and tags. Fields are automatically determined.Each row represents
a unique data point. `NA`'s are not supported and need to be removed. 
Timestamps should be located in column `time`.

Remember that time and tags are optional: InfluxDB uses the server’s local 
nanosecond timestamp in UTC if the timestamp is not included with the point.

```{r write_df}
# convert the existing xts-object to data.frame
df_data <- dplyr::bind_cols(time = zoo::index(xts_data), # timestamp
                            data.frame(xts_data)) %>% # coredata
  dplyr::mutate(info = "SampleDataMatrix", # add tag 'info'
                UnitTesting = TRUE, # add tag 'UnitTesting'
                n = row_number(), # add tag 'n'
                source = "df")  # add source 'df'

df_data

# write example data.frame to database
influx_write(con = con, 
             db = "mydb",
             x = df_data,
             time_col = "time", tag_cols = c("info", "UnitTesting", "n", "source"),
             measurement = "sampledata")
```

We can now check if the time series were successfully written:

```{r check_write_xts}
# check if measurements were succefully written
show_measurements(con = con, db = "mydb")
```

### Query data

To query the database, two functions `influx_query` and `influx_select` are available.
`influx_select` wraps around `influx_query` and can be useful for simple requests 
because it provides default query parameters. The return type can be configured 
to be of class `tibble` or of class `xts`.

#### Return tibbles

If `return_xts = FALSE` a list of tibbles per query statement is returned. Each tibble contains columns with statement_id, series_names, tags, time and fields.

```{r return_tibble}
# fetch time series data by using the helper function `influx_select`
result <- influx_select(con = con, 
                        db = "mydb", 
                        field_keys = "Open, High", 
                        measurement = "sampledata",
                        where = "source = 'df'",
                        group_by = "*",
                        limit = 10, 
                        order_desc = TRUE, 
                        return_xts = FALSE)

result
```

#### Return xts

If `return_xts = TRUE` a list of xts objects per query statement is returned. Because xts objects are basically matrices (which can store one data type only), a single xts object is created for each InfluxDB field. This ensures a correct representation of the field values data type (instead of getting all into a "character" matrix). InfluxDB tags are now xts attributes.

```{r return_xts}
# fetch time series data by using the helper function `influx_select`
result <- influx_select(con = con, 
                        db = "mydb", 
                        field_keys = "Open, High", 
                        measurement = "sampledata",
                        where = "source = 'xts'",
                        group_by =  "*",
                        limit = 10, 
                        order_desc = TRUE, 
                        return_xts = TRUE)

str(result)
```
#### Simplify InfluxDB response

In case the InfluxDB response is expected to be a single series only, 
we can flatten the list (`simplifyList = TRUE`) to directly get to the data.
This enhances a pipeable work flow.

```{r simplify_response}
result <- influx_select(con = con, 
                        db = "mydb", 
                        field_keys = "Open", 
                        measurement = "sampledata",
                        where = "source = 'df'",
                        group_by =  "*",
                        limit = 10, 
                        order_desc = TRUE, 
                        return_xts = FALSE, 
                        simplifyList = TRUE)

str(result)
```

## Contributions
This Git repository contains the latest contributions to the R package `influxdbr` and other code that will appear in the next [CRAN](https://cran.r-project.org/package=influxdbr) release.

Contributing to this package is easy. Just send a [pull request](https://help.github.com/articles/using-pull-requests/). Your PR should pass `R CMD check --as-cran`, which will also be checked by <a href="https://travis-ci.org/dleutnant/influxdbr">Travis CI</a> when the PR is submitted.

## Code of conduct
Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

## Citation

```{r citation, echo=FALSE, results='asis'}
citation("influxdbr")
```
